The Driving Forces Behind API Evolution

### 2015-05-20 thesis/paper.tex
Removed refactoring stuff from intro
review intro
Grammar in intro+moved RQs to meth

\section{Introduction} \label{introduction}
%API Design (and a little bit of ecosystems and a bit of problem statement)
As the software industry and the open-source movement continue to grow, the number of public APIs is steadily increasing. APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}. There is a consensus in that modifications to APIs could negatively impact the users of the API \cite{google_talk, mcdonnell2013empirical, robbes2012developers, henning2007api}. The main reason for this is that it requires the API users to update the application code, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}. Refactoring is the most common change that APIs undergo \cite{dig2005role, xing2006refactoring}. 
%Software Evolution 
In the discipline of software evolution, such updates to software are studied from an evolutionary standpoint. Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive changes \cite{lientz1980software}.

%Purpose
Modifications to deployed APIs may negatively impact its users. It is therefore important to investigate why these changes occur. Understanding the motives behind the changes could help API designers to  prevent potential future changes to their APIs. Before industry can safely include such information in their feedback loop, we must critically assess to what degree we can reverse engineer such motives.

%Gap in Literature
Studies that explore the intent behind API modifications exist \cite{hou2011exploring}. The area of programming language APIs is well-explored \cite{hou2011exploring, shi2011empirical}, but few studies that explore platform APIs exist \cite{robbes2012developers}. To the best of our knowledge, no studies that explore API evolution have until now been performed on embedded platform APIs.

%Purpose of the study
The goal of the study was twofold. Firstly, the aim was to explore what are the driving forces behind API evolution and secondly, to validate the results' level of correctness by comparing our findings with the case company's explanation of the changes. With this information, we could determine to what extent these change decisions can be reverse engineered. 
%Why this is important for the case company.
This study has many potential benefits for the case company. Identifying the types of changes that occur when an API evolves will improve communication and discussions regarding maintenance and evolution tasks. This improved communication could provide a common language that developers, users and management can use to discuss potential evolution of the APIs. Understanding the evolution theories could further assist understanding of how change will occur and how to plan for it. Lastly, by keeping a history of changes to an API over time, trends can be identified which could help with future API design.

>>>>

\section{Introduction} \label{introduction}
%1API Design (and a little bit of ecosystems and a bit of problem statement)
As the software industry and the open-source movement continue to grow, the number of public APIs is steadily increasing. APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}. There is a consensus in that modifications to APIs could negatively impact the users of the API \cite{google_talk, mcdonnell2013empirical, robbes2012developers, henning2007api}. The main reason for this is that it requires the API users to update the application code, thus causing a disruption in the application's software ecosystem \cite{messerschmitt2005software}. 
%2Software Evolution 
In the discipline of software evolution, such updates to software are studied from an evolutionary standpoint. Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive changes \cite{lientz1980software}.

%3Purpose
Modifications to deployed APIs may negatively impact its users. It is therefore important to investigate why these changes occur. Understanding the motives behind the changes could help API designers to  prevent potential future changes to their APIs. Before industry can safely include such information in their feedback loop, we must critically assess to what degree we can reverse engineer such motives.

%4Gap in Literature
Studies that explore the intent behind API modifications exist \cite{hou2011exploring}. The area of programming language APIs is well-explored \cite{hou2011exploring, shi2011empirical}, but few studies that explore platform APIs exist \cite{robbes2012developers}. To the best of our knowledge, no studies that explore API evolution have until now been performed on embedded platform APIs.

%5Purpose of the study
The goal of the study was twofold. Firstly, the aim was to explore what the driving forces behind API evolution are, and secondly, to validate the results' level of correctness by comparing our findings with the case company's explanation of the changes. With this information, we could determine to what extent these change decisions can be reverse engineered. 
%6Why this is important for the case company.
This study has many potential benefits for the case company. Identifying the types of changes that occur when an API evolves will improve communication and discussions regarding maintenance and evolution tasks. This improved communication could provide a common language that developers, users and management can use to discuss potential evolution of the APIs. Understanding the evolution theories could further assist understanding of how change will occur and how to plan for it. Lastly, by keeping a history of changes to an API over time, trends can be identified which could help with future API design.

%I would suggest that paragraph #6 is merged with paragraph 3. (I.e. move #6 in between #3 and #4). Otherwise we have a purpose in two places and the most important part of the purpose in the end of the intro, which isn't good.

%The first sentence of paragraph 6 is very subjective and doesn't really add much

%I also think the gap (#4) has to be re-written. Right now it doesn't say much at all. And the 2nd sentence makes no sense at all (2refs="well-explored" and 1ref="few")

%Otherwise really good... like the #6 a lot
